### 2014-11-08 tex/lazy.tex
adding the text for the field access

The rewrite rule to initialize a heap in the symbolic summarization
technique is shown in~\figref{fig:symInit}. Given the unitialized set
$\mathbb{UN}$ for field $f$, the $\mathit{min}_l$ function returns the
constraint location pair based on a lexical ordering of locations. The
init$_r$ method returns a new input reference $r_f$ while the
fresh$_f$ returns a new location of type $C$. The set $\rho$ contains
the set of reference location, $(r_a, l_a)$, pairs that the current
field may alias. The pair $(r_a, l_a)$ is contained in the set $ \rho
$ if $r_a$ is part of the input references initialized in the summary
heap, $r_a$ is in the pre-image of $l_a$, and the type of $l_a$ is the
same as the type of the field being initialized then the pair $(r_a,
l_a)$ is added to the $\rho$ set.

>>>>

The rewrite rule to initialize a heap in the symbolic summarization
technique is shown in~\figref{fig:symInit}. Given the unitialized set
$\mathbb{UN}$ for field $f$, the $\mathit{min}_l$ function returns the
constraint location pair based on a lexical ordering of locations. The
init$_r$ method returns a new input reference $r_f$ while the
fresh$_f$ returns a new location of type $C$. The set $\rho$ contains
the set of reference location, $(r_a, l_a)$, pairs that the current
field may alias. The pair $(r_a, l_a)$ is contained in the set $ \rho
$ if the following conditions hold: (i) $r_a$ is part of the input
references initialized in the summary heap, (ii) $r_a$ is in the
pre-image of $l_a$, (iii) and the type of $l_a$ is the same as the
type of the field being initialized.

### 2014-11-08 tex/precise.tex
re-orging
remove noisy files and more info of sets on teh examples
reorging the figure
precise
Grouped Figure 8 and Figure 9
Grouped figures 10 and 12
adding the text for the field access

\section{GSE with Heap Summaries}

@@

@@

\input{summarize-precise}
\input{precise-fig}

>>>>

\subsection{Accessing a Field Reference}

\input{precise-fig}

\begin{figure*}[t]
\begin{center}
\setlength{\tabcolsep}{50pt}
\begin{tabular}[c]{cc}
\usebox{\boxPFAFW} & 
%\scalebox{0.91}{\input{faYHeap.pdf_t}} &
\scalebox{0.91}{\input{fwXHeap.pdf_t}} \\ \\
(a) & (b)
\end{tabular}
\end{center}
\caption{field access for this.y and field write for this.x = this.y}
\label{fig:fHeap}
\end{figure*}

There are two rewrite rules in~\figref{fig:fHeap}(a), one for field
access and the other for field write. Let us consider the rewrite rule
for field access. The first check we perform is whether there exists a
constraint location pair for the $r$ being accessed such that the
location is not null and the constraint when conjuncted with the
global constraint is satisfiable. Next we extract all possible
constraints under which $r$ points to a null location such that the
constraint is satisfiable under the current global constraint,
$\phi_g$. The negation of these constraints are added to the global
constraint to create a new global constraint $\phi_g^\prime$. The
update to the global constraint ensures that access of the field $f$
happens only on non-null locations. The type $C$ of the field is
extracted and passed to rewrite rule that performs the initialization
of the symbolic heap. The initialization rules are described earlier
in this section.

Recall that during the initialization the rewrite rules
in~\figref{fig:symHeap} add input references that map to fields being
initialized.  Once the initialization is complete, however, we create
a new local reference $r^\prime$. An important property of the
references in the bi-partiate graph is that they are
\emph{immutable}. Hence we de-reference the initialized input
reference, assign its value to the the new local reference, and return
the local reference. In order to de-reference a field $r.f$ we define
a helper function which is called the value set.

@@

In the post-condition of the rewrite rule we assign
the value set of input reference $r$ to the local reference $r^\prime$
and return the local reference $r^\prime$ in the next state.

Consider the graph shown in~\figref{fig:fHeap}(b) the reference
$r_2^i$ is created during the initialization of $\mathit{this}.y$. The
reference that is returned during the access of the field, however, is
$r_3^s$. The reference $r_3^s$ points to the value set of $r_2^i$
which are: $(\phi_{2a}, l_\mathit{null})$, $(\phi_{2b}, l_2)$, and
$(\phi_{2c}, l_1)$. The values of the constraints $\phi_{2a}$,
$\phi{2b}$, and $\phi_{2c}$ are defined in~\figref{fig:initHeap}(d).

\subsection{Writing to a Field}

@@

\begin{comment}
\begin{figure}[t]
\begin{center}
\begin{tabular}[c]{l}
$\Psi_x = \{ (true, l_0, r_1^i) \}$\\
$ST (L, r_3^s, \phi, \phi_g)$ \\
$\theta = \{ (\phi_{2a}\; l_\mathit{null} ) (\phi_{2b}\; l_2) (\phi_{2c}\; l_1) \}$\\
$ST(L, r_0, \phi, \phi_g)$\\
$\theta = \{ \}$\\
\end{tabular}
\end{center}
\caption{field write for this.x = this.y sets}
\label{fig:faHeapSets}
\end{figure}
\end{comment}

\subsection{Equality and InEquality of References}

\input{precise-eq}

\newsavebox{\boxPEX}
\savebox{\boxPEX}{
\begin{tabular}[c]{l}
$L(r_1^i) = \{ (\phi_{1a}\; l_\mathit{null})\; (\phi_{1b}\; l_1) \}$ \\
$L(r_2^i) = \{ (\phi_{2a}\; l_\mathit{null}),\; (\phi_{2b}\; l_2),\; (\phi_{2c}\; l_1) \} $\\
  $\theta_0 = \{ \} $\\
$\theta_1 = \{ \phi_{2b}\} $\\ \hline
Equals true \\
$\theta_\alpha = \{ (\phi_{1a}\; \wedge\; \phi_{2a} ) (\phi_{1b}\; \wedge\; \phi_{2c} ) \}$\\
$\phi^\prime = \mathit{true} \wedge [ (\phi_{1a}\; \wedge\; \phi_{2a} )\vee (\phi_{1b}\; \wedge\; \phi_{2c} ) ] \wedge \neg\phi_{2b} $\\ \hline
Equals false \\
$\theta_\alpha = \{ (\phi_{1a}\; \implies\; \neg\phi_{2a} ) (\phi_{1b}\; \implies\; \neg\phi_{2c} ) \}$\\
$\phi^\prime = \mathit{true} \wedge  (\phi_{1a}\; \implies\; \neg\phi_{2a} )\wedge (\phi_{1b}\; \implies\; \neg\phi_{2c} )  \wedge \phi_{2b} $\\ \hline
\end{tabular}}

\begin{figure*}
\begin{tabular}[c]{cl}
\usebox{\boxPEQ} & \usebox{\boxPEX} \\ \\
(a) & (b) \\
\end{tabular}
\caption{equals true for this.x == this.y}
\label{fig:eqs-true}
\end{figure*}
